Bayesian exponential random graph modeling of KWL Burial network

### 2020-07-03 analysis/paper/paper.Rmd
edit method section

@@

MCMC simulation can estimate the posterior distribution of interest by of random sampling without the need of normal distribution for the prior and likelihood. MCMC is a random probability distribution that describes a sequence of events or transitions (chain) from one state to another state following probabilistic rules. In Bayesian ERGMs, MCMC first selects a set of edges (or a set of empty pair of actors) with equal probability, and than switch to a pair of actors at random within that chosen set [@Caimo2011]. In our case, we set the number of chains to six. For each chain, the number of burn-in iterations is 200 and the number of iterations after the burn-in is 2000. We set the number of iterations used to simulate a network y′ at each iteration to 10,000. The models are assessed by goodness-of-fit (GOF) diagnostics in the Bayesian framework, where the observed network is compared with the set of networks simulated from the estimated posterior distribution of the parameters of the model [@Caimo2011; @Caimo2017]. This provides a statistical way to check how well the estimated posterior parameter distribution can reproduce networks similar to the general structural features of the observed network.

<!--Model fitting and comparison to alternative approaches-->

@@

Normal distribution 𝜃 ∼ Nd (𝜇prior , Σprior ) is viewed as a suitable prior model for the model parameters of interests in network analysis if there is no previous observation for a network[@Caimo2017]. Since our original data presents a pattern of dense ties, we specified the prior based on our observation that assumes a high density and high transitivity network.

>>>>

<!--Bayesian approaches-->

@@

<!--Model fitting and comparison-->

MCMC simulation can estimate the posterior distribution of interest by of random sampling without the need of normal distribution for the prior and likelihood. MCMC is a random probability distribution that describes a sequence of events or transitions (chain) from one state to another state following probabilistic rules. In Bayesian ERGMs, MCMC first selects a set of edges (or a set of empty pair of actors) with equal probability, and than switch to a pair of actors at random within that chosen set [@Caimo2011]. In our case, we set the number of chains to six. For each chain, the number of burn-in iterations is 200 and the number of iterations after the burn-in is 2000. We set the number of iterations used to simulate a network y′ at each iteration to 10,000. The models are assessed by goodness-of-fit (GOF) diagnostics in the Bayesian framework, where the observed network is compared with the set of networks simulated from the estimated posterior distribution of the parameters of the model [@Caimo2011; @Caimo2017]. This provides a statistical way to check how well the estimated posterior parameter distribution can reproduce networks similar to the general structural features of the observed network. Our observed networks, pre-European and post-European networks, followed the normal distribution that is a suitable prior model in network analysis that assumes networks with low density and high transitivity commonly observed in real world [@Caimo2017]. Since our original data implies higher transitivity due to potentially multiple groups having the same kind of burial good in common, we specified the prior based on our observation with higher transitivity.

@@
